---
title: "Gun Control Chi Square"
author: "Callie Steffen, Vanessa Guenther, Renee Albreight"
date: "11/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm Callie and I'm adding some text here to see if my collaborators can get my files

Its callie again and im updating some text 

Hey Cal LeiL Nice sweater

Hey tyler thank you so muchhhhhhhhh


```{r}

#####Loading Packages

library(tidyverse)
library(knitr)
library(kableExtra)
library(pwr)

###reading in the csv data file and getting some summary counts

gcdf <-read_csv("gc_df.csv")

get_guns<- gcdf %>% 
  filter(gender !="NA", make_get_guns != "NA") %>% 
  count(gender,make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns)<- c("female", "male")
```
I'm the collaborator (Tyler Cobian) I'm doing to perform a Chi^2^

I think the Chi^2^ will answer the question as to if there is association between gender and opionion on gun control. Do men and women think differently about if it should be easier or harder to get a gun?

```{r}
guns_prop<- prop.table(as.matrix(get_guns), 1)
guns_prop

#perform Chi-square

guns_x2<- chisq.test(get_guns)
guns_x2



```

Recomended government action differs significantly for males and females ($\chi^2$(`r gun_x2$parameter`)=........, p<0.001)
















